Comprehensive Quality Awareness Automated Semantic Web Service Composition

### 2017-03-28 paper.tex
update

\documentclass{llncs}
\usepackage[ruled,vlined]{algorithm2e}
\usepackage{color,graphicx,epstopdf,changepage,amsmath,multirow}
\usepackage[justification=centering]{caption}
\SetAlgoCaptionSeparator{.\space}
\renewcommand\AlCapFnt{\normalfont\scshape}
\setlength{\algomargin}{0.7cm}

@@

Step 2: This composition task is used to discover all task-related service candidates using a greedy search adopted from \cite{ma2015hybrid}. This algorithm keeps adding outputs of the evocable services as available outputs, and these available outputs are used to discovery new services from service repository and be updated with the outputs of these discovered services. This loop process does not stop until no service is satisfied by the available outputs. During this greedy search, an ontology-based cache is initialised, which stores the concept similarities of inputs and outputs of task-related candidate that are further demonstrated in SubSect. \ref{indexCache}.

Step 3: Particle initialisation and serivce-to-index mapping. In the initialisation, each particle's position size is determined by the size of task-related service candidates. Meanwhile, each service candidate is mapped to an index of a particle’s position vector (each vector have a weight value that falls between 0.0 and 1.0). After that, all the service candidates are put in a queue and sorted according to their corresponding weight values in a descending order. This procedure are a part of  Algorithm \ref{novelSteps} below. This sorted queue is used as one of the input of a forward decoding algorithm \ref{graph_building} to create a weighted graph using ontology-based cache in Step 2. In addition, this forward graph building Algorithm can lead to more services and edges connected to the graph, which should be removed at last.

Step 4. Follows left steps of algorithm \ref{novelSteps} as the same as the standard PSO steps, Besides that, particles' fitness is calculated on the decoded weight DAGs.

\subsection{Ontology-based Index Cached Optimisation}\label{indexCache}
our PSO-based approach demands decoding processes from optimised queues to weighted DAGs, a bottleneck of efficiently constructing weighted DAGs lie in building required information of edges, which is related to the cost of $fullmatch$
$(a \Rightarrow b)$ identifications and $sim(a, b)$ calculations between input-related and output-related concepts of service candidates. To efficiently construct weighted DAGs, we calculate $sim(a, b)$ of all $fullmatch(a \Rightarrow b)$ interleaving with the greedy search discussed in Sect \ref{PSO_based_approach}. This information is stored in a table structure with special $X$ value if no $fullmatch(a \Rightarrow b)$ is satisfied. Therefore, this optimised cache contributes to less and constant time for weighted DAG building through the evolutionary process.

\begin{algorithm}
 \SetKwInOut{Input}{Input}\SetKwInOut{Output}{Output}
 \SetKwFunction{generateWeightedGraph}{generateWeightedGraph}
 \SetKwProg{Procedure}{Procedure}{}{}
 \LinesNumbered
 \SetNlSty{}{}{:}
 Randomly initialise each particle in the swarm\;
  \While {max. iterations not met}{
     \ForEach{particles in the swarm}{
     Map service candidates to particle's position vector\;
     Create a service queue and sort it by position vectors' weights\;
     Decode the service into a weighted DAG \;
	 Calculate the $Weighted DAG$ fitness value\;

      \eIf{fitness value better than \emph{pBest}}{    
        Assign current fitness as new \emph{pBest}\;
       }{
        Keep previous \emph{pBest}\;
       }	
     }
    Assign best particle's \emph{pBest} value to \emph{gBest}, if better than \emph{gBest}\;
 	Calculate the velocity of each particle\;
  	Update the position of each particle\;
  }
\caption{Steps of PSO-based service composition technique \cite{da2016particle}.}
\label{novelSteps}
\end{algorithm} 
\begin{algorithm}
 \SetKwInOut{Input}{Input}\SetKwInOut{Output}{Output}
 \SetKwFunction{createWeightedDAG}{createWeightedDAG}
 \SetKwProg{Procedure}{Procedure}{}{}
 \LinesNumbered
 \SetNlSty{}{}{:}
  \Procedure{\createWeightedDAG{}}{
 \Input{ $I_T$, $O_T$, $queue$, $Cache$}
 \Output{WG}
 $WG = (V, E)$\;
 $V \leftarrow$ \{$Start$, $End$ \} \;
 $OutputSet \leftarrow$ \{$I_{T}$\}\;
  \While { $O_{T}$ $\notin$ $OutputSet$  and $queue !=null$}{
     \ForEach{$S$ in $queue$}{
      \uIf{$fullmatch(a \Rightarrow b)$$\wedge$ $(a \in OutputSet)$ $\wedge$ $(b \in I_{S})$ $\wedge$ $\mid fullmatch(a \Rightarrow b) \mid = \mid I_{S} \mid$}{    
    		 \ForEach{$fullmatch(a \Rightarrow b)$}{
    		$sim(a,b) \leftarrow$ query $IndexCache$\;
 			$sm(a,b) \leftarrow$ $( type(a,b), sim(a,b))$\;
              }
        $sm_{e} \leftarrow$ aggregate \{ $sm(a,b)$ \}\;
        $E \leftarrow$ add $e$\;
        $V \leftarrow$ add $S$\;
        $OutputSet$ add \{$O_{S}$\}\;    
        $queue$.remove $S$\;
       }	
     }
  }
 remove $dangling nodes$\; 
 remove $dangling edges$\;
 \KwRet $WG$\;
 }
 \caption{Create a weighted DAG from a  sorted queue.}
\label{graph_building}
\end{algorithm}

\section{Experiment Design}\label{experiment_design}
In this section, a quantitative evaluation approach is adopted in our experiment design. The objectives of the evaluation are to $(1)$ measure the effectiveness of the comprehensive quality model in automated semantic web service composition approach; and $(2)$ compare solutions generated by a recent QoS-ware evaluation approach \cite{ma2015hybrid,da2016genetic} with our evaluation method proposed in the paper; and $(3)$ compare our PSP-based method with one existing GP-based approach \cite{ma2015hybrid}.

@@

\section{Results and Analysis}\label{results_analysis}
\subsection{Comparison Test for Comprehensive Quality Evaluation Model and QoS Evaluation Model}\label{comparisonTest}

@@

>>>>

\documentclass{llncs}
\usepackage[ruled,vlined,linesnumbered]{algorithm2e}
\usepackage{color,graphicx,epstopdf,changepage,amsmath,multirow}
\usepackage[justification=centering]{caption}
\SetAlgoCaptionSeparator{.\space}
\renewcommand\AlCapFnt{\normalfont\scshape}
\setlength{\algomargin}{0.7cm}

@@

Step 2: This composition task is used to discover all task-related service candidates using a greedy search adopted from \cite{ma2015hybrid}. During this greedy search, an ontology-based cache ($Cache$) is initialised, which stores the concept similarities of inputs and outputs of task-related candidates.

Step 3 and Step 4: These two steps follow the stardard PSO steps \cite{shi2001particle} except some differences that lie in  particles initialisation and decoding process. These two differences are related to sort a service queue using a serivce-to-index mapping for a particle' position vectors and evaluate the fitness of a particle after decoding this serivce queue into a weighted DAG respectively, which are further addressed in Algorithm \ref{novelSteps} and \ref{graph_building} in SubSect \ref{POS-based_algomargin}.

.

\subsection{PSO-based approach algorithm}\label{POS-based_algomargin}
The overall algorithm investigated here is made up of the PSO-based web service composition algorithm \ref{novelSteps} and the decoding algorithm \ref{graph_building}. In algorithm \ref{novelSteps}, the  steps $4$, $5$, $6$ and $7$ are different steps from those of stardard PSO. First, each particle's position size is determined by the size of task-related service candidates generated by a greedy search. This greedy search algorithm keeps adding outputs of the evocable services as available outputs, and these available outputs are used to discovery task-related services from service repository and be updated with the outputs of these discovered services. This loop process does not stop until no service is satisfied by the available outputs. Second, each service candidate is mapped to an index of a particle’s position vector, where each vector have a weight value that falls between 0.0 and 1.0. This a service-to-index mapping for position vectors discussed in Step 3 in SubSect \ref{PSO_based_approach}. Third, all the service candidates are put in a queue and sorted according to their corresponding weight values in a descending order. Fourth, this sorted queue is used as one of the input of a forward decoding algorithm \ref{graph_building} to create a weighted DAG, this fitness value of this weighted DAG is the fitness value of the particle.
\begin{algorithm}
 %\LinesNumbered
 \SetKwInOut{Input}{Input}\SetKwInOut{Output}{Output}
 \SetKwFunction{generateWeightedGraph}{generateWeightedGraph}
 \SetKwProg{Procedure}{Procedure}{}{}
 \SetNlSty{}{}{:}
 Randomly initialise each particle in the swarm\;
  \While {max. iterations not met}{
     \ForEach{particles in the swarm}{
     Map service candidates to particle's position vector\;
     Create a service queue and sort it by position vectors' weights\;
     Create the service into a weighted DAG \;
	 Calculate the $Weighted DAG$ fitness value\;

      \eIf{fitness value better than \emph{pBest}}{    
        Assign current fitness as new \emph{pBest}\;
       }{
        Keep previous \emph{pBest}\;
       }	
     }
    Assign best particle's \emph{pBest} value to \emph{gBest}, if better than \emph{gBest}\;
 	Calculate the velocity of each particle\;
  	Update the position of each particle\;
  }
\caption{Steps of PSO-based service composition technique \cite{da2016particle}.}
\label{novelSteps}
\end{algorithm}

This Algorithm  \ref{graph_building}is a forward graph graph buidling algorithm based on \cite{blum1997fast}. This algorthm take an input of the sorted service queues discussed above, and service queues with diferent order is possible to create different weighted DAGs as composition solutions. In additon. $I_{T}$, $O_{T}$ and $Cache$ are also taken as inputs. Firstly, $Start$ and $End$ are added to V of WG initialization, $OutputSet$ is created with $I_{T}$.  If all the inputs of first $S$ popped from $queue$ can be satisfied by provided outputs of $OutputSet$, this $S$ is added to $V$ and its outputs are added to $OutputSet$. Meanwhile, $sm_{e}$ is calcated based on the aggregation value of $sm(a, b)$

Otherwise,  next $S$ popped from the $queue$ is to be considered. These steps are not stopped until all  $O_{T}$ can satisfied from $Outputset$ or queue is null.

can lead to more services and edges connected to the graph, which should be removed at last.

\begin{algorithm}
 \SetKwInOut{Input}{Input}\SetKwInOut{Output}{Output}
 \SetKwFunction{createWeightedDAG}{createWeightedDAG}
 \SetKwProg{Procedure}{Procedure}{}{}
 %\LinesNumbered
 \SetNlSty{}{}{:}
  \Procedure{\createWeightedDAG{}}{
 \Input{ $I_T$, $O_T$, $queue$, $Cache$}
 \Output{WG}
 $WG = (V, E)$\;
 $V \leftarrow$ \{$Start$, $End$ \} \;
 $OutputSet \leftarrow$ \{$I_{T}$\}\;
  \While { all $O_{T}$ do not satisfied by $OutputSet$}{
     \ForEach{$S$ in $queue$}{
      \uIf{all $I_{S}$ satisfied by $OutputSet$}{    
    		 \ForEach{$I_{S}$}{
		$sm(a \in Outputset, b \in I_{S}) \leftarrow$ query $Cache$\;
              }
        Calculate $sm_{}$\;
        $E \leftarrow$ add $e$\;
        $V \leftarrow$ add $S$\;
        $OutputSet$ add \{$O_{S}$\}\;    
        $queue$.remove $S$\;
       }	
     }
  }
 remove $dangling nodes$\; 
 remove $dangling edges$\;
 \KwRet $WG$\;
 }
 \caption{Create a weighted DAG from a  sorted queue.}
\label{graph_building}
\end{algorithm}

\section{Experiment Study}\label{experiment_design}
In this section, a quantitative evaluation approach is adopted in our experiment design. The objectives of the evaluation are to $(1)$ measure the effectiveness of the comprehensive quality model in automated semantic web service composition approach; and $(2)$ compare solutions generated by a recent QoS-ware evaluation approach \cite{ma2015hybrid,da2016genetic} with our evaluation method proposed in the paper; and $(3)$ compare our PSP-based method with one existing GP-based approach \cite{ma2015hybrid}.

@@

\subsection{Comparison Test for Comprehensive Quality Evaluation Model and QoS Evaluation Model}\label{comparisonTest}

@@

\subsection{Further Discussion}\label{discuss1}
